Context-dependent consequences of including lagged effects in demographic models

### 2022-08-04 docs/paper.Rmd
added bdffp tech series to ackngmnts

We thank **,** \_, \_\_\_ and \_\_\_ anonymous reviewers for helpful discussions and comments on the manuscript.
We thank Sam Levin for his help with the `ipmr` package.
Financial support was provided by the U.S.
National Science Foundation (awards \_\_\_\_, and \_\_\_\_).
The authors declare no conflicts of interest.

@@

```{r lambdas, results='asis'}
lambda_table %>% 
  mutate(habitat = toupper(habitat)) %>% 
  mutate(across(c(est, lower, upper), ~format(round(.,4)))) %>% 
  mutate(lambda = glue::glue("{est} ({lower}, {upper})")) %>%
  mutate(ipm = str_replace_all(
    ipm,
    c(
      "det" = "Deterministic",
      "stoch" = "Stochastic, kernel-resampled",
      "DLNM" = "Stochastic, parameter-resampled"
    )
  )) %>% 
  select(IPM = ipm, Habitat = habitat, "$\\lambda$" = lambda) %>% 
pandoc.table(
  digits = 5,
  keep.trailing.zeros = TRUE,
  justify = c("left", "left", "right"),
  full_width = FALSE,
  caption = "(\\#tab:lambdas) Population growth rates for continuous forest (CF) and forest fragments (FF) under different kinds of IPMs with bootstrapped, bias-corrected, 95% confidence intervals."
)

>>>>

We thank **,** \_, \_\_\_ and \_\_\_ anonymous reviewers for helpful discussions and comments on the manuscript.
We thank Sam Levin for his help with the `ipmr` package.
Financial support was provided by the U.S.
National Science Foundation (awards \_\_\_\_, and \_\_\_\_).
This article is publication no. -- -- in the BDFFP Technical series.
The authors declare no conflicts of interest.

@@

```{r lambdas, results='asis'}
lambda_table %>% 
  mutate(habitat = toupper(habitat)) %>% 
  mutate(across(c(est, lower, upper), ~format(round(.,4)))) %>% 
  mutate(lambda = glue::glue("{est} ({lower}, {upper})")) %>%
  mutate(ipm = str_replace_all(
    ipm,
    c(
      "det" = "Deterministic",
      "stoch" = "Stochastic, kernel-resampled",
      "dlnm" = "Stochastic, DLNM"
    )
  )) %>% 
  select(IPM = ipm, habitat, lambda) %>% 
  pivot_wider(names_from = "habitat", values_from = lambda) %>%

pandoc.table(
  digits = 5,
  keep.trailing.zeros = TRUE,
  justify = c("left", "right", "right"),
  full_width = FALSE,
  caption = "(\\#tab:lambdas) Population growth rates (lambda) for continuous forest (CF) and forest fragments (FF) under different kinds of IPMs with bootstrapped, bias-corrected, 95% confidence intervals."
)
#TODO: in caption possibly explain that lambdas are calculated differently for deterministic and stochastic models
```
